\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-07-23 manuscript/manuscript.tex
updated affiliation names
updated affiliations

% Title
\title{
    \usefont{OT1}{bch}{b}{n}
    \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt]
    \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\
}
\selectlanguage{english}
\usepackage{authblk}
\author[1]{Eddie Guo}
\author[1]{Pouria Torabi}
\author[2]{Daiva Nielsen}
\author[3]{Matthew Pietrosanu}
\affil[1]{\small Neuroscience and Mental Health Institute, University of Alberta}
\affil[2]{\small School of Human Nutrition, McGill University}
\affil[3]{\small Department of Mathematical and Statistical Science, University of Alberta}

>>>>

% Title
\title{
    \usefont{OT1}{bch}{b}{n}
    \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt]
    \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\
}
\selectlanguage{english}
\usepackage{authblk}
\author[1,2]{Eddie Guo}
\author[1,2]{Pouria Torabi}
\author[3]{Daiva Nielsen}
\author[4]{Matthew Pietrosanu}

\renewcommand\Affilfont{\scriptsize}
\affil[1]{University of Alberta}
\affil[2]{Youreka Canada}
\affil[3]{School of Human Nutrition, McGill University}
\affil[4]{Department of Mathematical and Statistical Sciences, University of Alberta}
